---
title: "INED "
author: "Joseph Siegmund"
date: "1/12/2024"
output: html_document
---

set working directory and upload dataset
```{r}
setwd("/Users/jsiegm1/Documents/INED interview/donnees")
d <- read.csv("data.csv" , header=T, sep= ";")


```


```{r}

install.packages("visdat")
install.packages("skimr")
install.packages("DataExplorer")
install.packages("tidyverse")
install.packages("VIM")

library(purrr)
library(mice)
library(VIM)
library(visdat)
library(skimr)
library(DataExplorer)
library(dplyr)
library(ggplot2)
```



take a look at the dataset formatting 
```{r }
colnames(d)
str(d)
```

reshape the data, create new variables 

```{r }
df1 <- d %>% 
  select(id, `annee_tentative.1`, `traitement_tentative.1`) %>% 
  rename(Year= annee_tentative.1, Treatment= traitement_tentative.1) %>% 
  mutate(Tentative= 1)

df2 <- d %>% 
  select(id, `annee_tentative.2`, `traitement_tentative.2`) %>% 
  rename(Year= annee_tentative.2, Treatment= traitement_tentative.2) %>% 
  mutate(Tentative= 2)

df3 <- d %>% 
  select(id, `annee_tentative.3`, `traitement_tentative.3`) %>% 
  rename(Year= annee_tentative.3, Treatment= traitement_tentative.3) %>% 
  mutate(Tentative= 3)

df4 <- d %>% 
  select(id, `annee_tentative.4`, `traitement_tentative.4`) %>% 
  rename(Year= annee_tentative.4, Treatment= traitement_tentative.4) %>% 
  mutate(Tentative= 4)

df5 <- d %>% 
  select(id, `annee_tentative.5`, `traitement_tentative.5`) %>% 
  rename(Year= annee_tentative.5, Treatment= traitement_tentative.5) %>% 
  mutate(Tentative= 5)


df6 <- d %>% 
  select(id, `annee_tentative.6`, `traitement_tentative.6`) %>% 
  rename(Year= annee_tentative.6, Treatment= traitement_tentative.6) %>% 
  mutate(Tentative= 6)


df7 <- d %>% 
  select(id, `annee_tentative.7`, `traitement_tentative.7`) %>% 
  rename(Year= annee_tentative.7, Treatment= traitement_tentative.7) %>% 
  mutate(Tentative= 7)


df8 <- d %>% 
  select(id, `annee_tentative.8`, `traitement_tentative.8`) %>% 
  rename(Year= annee_tentative.8, Treatment= traitement_tentative.8) %>% 
  mutate(Tentative= 8)

df9 <- d %>% 
  select(id, `annee_tentative.9`, `traitement_tentative.9`) %>% 
  rename(Year= annee_tentative.9, Treatment= traitement_tentative.9) %>% 
  mutate(Tentative= 9)

df10 <- d %>% 
  select(id, `annee_tentative.10`, `traitement_tentative.10`) %>% 
  rename(Year= annee_tentative.10, Treatment= traitement_tentative.10) %>% 
  mutate(Tentative= 10)
```

create new data frame 
arrange by id 

```{r }
dff <- bind_rows(df1, df2, df3, df4, df4, df6, df7, df8, df9, df10)
dff <- dff %>%  arrange(id)

  
```

Check for missing
Missing at random
1540 total observations
773 obs missing in Year
686 obos missing in treatment 


```{r }
str(dff)
skim(dff)

```

 handle missing & impolausible data
 
Treatment 686  missing 
Treatment 686 missing both Year and Treatment
Year 773 missing 

There are not enough varibles to justify mulitple imputation. 
observations missing both Year and Treatmnet omitted 
Double check with data manager for missing treatments 

1540 total observations - 686 missing (treatment) = 854
1540 total observations - 773 missing (Year) = 776 obs 
no_na = 767 obs

Dont forget to add implausible data!

154 total people 

```{r }
dff %>%  filter(is.na(Treatment))
dff %>%  filter(is.na(Year))

missing_both <- dff %>% filter(is.na(Treatment) & is.na(Year))
missing_year <- dff %>% filter(is.na(Year))

dff_missing <- dff
dff_complete <- dff %>%filter(!is.na(Treatment) & !is.na(Year))
skim(dff_complete)
unique(dff_complete$id)

prop.table(table(dff_missing$Year))
prop.table(table(dff_complete$Year))


```

 NAs  appear to be missing at random
Here we will create:
labels, 
factors, 
new variables

Change Treatment,
Year to factor and create labels
Subset first tentative to see if new attempts are increasing over time


95			
2017	97			
2018	103			
2019	99			
2020	102			
2021	99			
2022	80			
avant_2005	92	


<2005	92			
2005-2016	95			
2017	97			
2018	103			
2019	99			
2020	102			
2021	99			
NA	80	

```{r }
final <- dff_complete
summary(final$Year)
unique(final$Year)
skim(final)

final %>% count(Year)
final %>% count(Year_factored)
```


```{r }
final$Year_factored <- factor (final$Year, 
            levels = c("avant_2005", "2005-2016", "2017", "2018", "2019", "2020", "2021", "2022"), 
            labels = c("<2005", "2005-2016", "2017", "2018", "2019", "2020","2021", "2022")
                          )



summary(final$Year_factored)

final$Treatment_factored <- factor(final$Treatment, 
                        levels = c( "traitement.1", "traitement.2", "traitement.3","traitement.4"),
                        labels= c("I", "II","III", "IV"))

summary(final$Treatment_factored) 


```


create data base filtering by first tentative

```{r }

first_tentative <- final %>% filter(Tentative==1)

```

descriptive statistics 


```{r }
library(gtsummary)

final %>%
  select(Year_factored, Treatment_factored, Tentative) %>% 
  tbl_summary( 
    by = Treatment_factored,
    statistic = list(Tentative ~ "{mean} ({sd})"),
    type = list(Tentative ~ "continuous"), 
    label = Year_factored ~ "Year", 
    missing = "no"
  ) %>%
  italicize_levels() %>%  
  bold_labels() %>% 
  add_p() %>% 
  add_stat_label() %>% 
  add_overall %>% 
  modify_spanning_header(c("stat_1","stat_2", "stat_3", "stat_4") ~ "Treatment Type") %>%   modify_caption("AMP Outside French Framework Descriptive Statistics") 


```


```{r }
library(gtsummary)

first_tentative %>%
  select(Year_factored, Treatment_factored) %>% 
  tbl_summary( 
  # Specify the variable type
    missing = "no"
  ) %>%
  italicize_levels() %>%  
  bold_labels() %>% 
  modify_caption("AMP Outside French Framework Descriptive Statistics")


```





```{r }
library(ggplot2)
final$Treatment_factored <- relevel(final$Treatment_factored, ref="I")
ggplot(final, aes(Treatment_factored)) + geom_bar(aes(fill=Treatment_factored)) + 
  ggtitle("Treatement distribution of the patients")



```


```{r }
ggplot(final, aes(Tentative, Treatment_factored)) + geom_boxplot() + ylab("Treatmnet") +
  labs(title = "Tentatives distribution of the patients",
              subtitle = "by treatment",
              caption = "Data source: INED AMP study")



```



```{r }




```

statistical test

```{r }

```
